---
title: "11_18_meeting_report"
author: "Siyang Ni"
date: "2022-11-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading datasets

```{r}
setwd("D:/research/Monitoring-The-Future/mtf_19_12")

load("D:/research/Monitoring-The-Future/mtf_19_12/DS0001/37841-0001-Data.rda")
core <- da37841.0001
rm(da37841.0001)

load("D:/research/Monitoring-The-Future/mtf_19_12/DS0002/37841-0002-Data.rda")
ds2 <- da37841.0002
rm(da37841.0002)

load("D:/research/Monitoring-The-Future/mtf_19_12/DS0003/37841-0003-Data.rda")
ds3 <- da37841.0003
rm(da37841.0003)

load("D:/research/Monitoring-The-Future/mtf_19_12/DS0004/37841-0004-Data.rda")
ds4 <- da37841.0004
rm(da37841.0004)

load("D:/research/Monitoring-The-Future/mtf_19_12/DS0005/37841-0005-Data.rda")
ds5 <- da37841.0005
rm(da37841.0005)

load("D:/research/Monitoring-The-Future/mtf_19_12/DS0006/37841-0006-Data.rda")
ds6 <- da37841.0006
rm(da37841.0006)

load("D:/research/Monitoring-The-Future/mtf_19_12/DS0007/37841-0007-Data.rda")
ds7 <- da37841.0007
rm(da37841.0007)

load("D:/research/Monitoring-The-Future/mtf_19_12/DS0008/37841-0008-Data.rda")
ds8 <- da37841.0008
rm(da37841.0008)

load("D:/research/Monitoring-The-Future/mtf_19_12/DS0009/37841-0009-Data.rda")
ds9 <- da37841.0009
rm(da37841.0009)

```

## Delinquency Variables

Load relevant packages

```{r}
library(epiDisplay)
```

### 00650:#X/12MO R TCKTD

Within the LAST 12 MONTHS, how many times, if any, have you received a ticket (OR been stopped and warned) for moving violations, such as speeding, running a stop light, or improper passing?

0="None" 1="Once" 2="Twice" 3="Three times" 4="Four or more times"

```{r}
tab1(core$V2197, cum.percent = TRUE)
tab1(ds2$V1197, cum.percent = TRUE)
tab1(ds3$V2197, cum.percent = TRUE)
tab1(ds4$V3197, cum.percent = TRUE)
tab1(ds5$V4197, cum.percent = TRUE)
tab1(ds6$V5197, cum.percent = TRUE)
tab1(ds7$V6197, cum.percent = TRUE)
```

### 06520:FRQ FIGHT PARNTS

how often have you . . . argued or had a fight with either of your parents?

1="Not At All" 2="Once" 3="Twice" 4="3 or 4 Times" 5="5 or More Times"
Data from the Western Region intentionally obliterated.

```{r}
tab1(ds3$V2279, cum.percent = TRUE)
```

### 06530:FRQ HIT SUPRVISR

During the LAST 12 MONTHS, how often have you . . . hit an instructor or supervisor?

1="Not At All" 2="Once" 3="Twice" 4="3 or 4 Times" 5="5 or More Times"

```{r}
tab1(ds3$V2280, cum.percent = TRUE)
```

### 06540:FRQ FGT WRK/SCHL

During the LAST 12 MONTHS, how often have you . . . gotten into a serious fight in school or at work?

1="Not At All" 2="Once" 3="Twice" 4="3 or 4 Times" 5="5 or More Times"

```{r}
tab1(ds3$V2281, cum.percent = TRUE)
```

### 06550:FRQ GANG FIGHT

During the LAST 12 MONTHS, how often have you . . . taken part in a fight where a group of your friends were against another group?

1="Not At All" 2="Once" 3="Twice" 4="3 or 4 Times" 5="5 or More Times"

```{r}
tab1(ds3$V2282, cum.percent = TRUE)
```

### 06560:FRQ HURT SM1 BAD

During the LAST 12 MONTHS, how often have you . . . hurt someone badly enough to need bandages or a doctor?

1="Not At All" 2="Once" 3="Twice" 4="3 or 4 Times" 5="5 or More Times"

```{r}
tab1(ds3$V2283, cum.percent = TRUE)
```

### 06570:FRQ THREAT WEAPN

During the LAST 12 MONTHS, how often have you . . . used a knife or gun or some other thing (like a club) to get something from a person?

1="Not At All" 2="Once" 3="Twice" 4="3 or 4 Times" 5="5 or More Times"

```{r}
tab1(ds3$V2284, cum.percent = TRUE)
```

### 06580:FRQ STEAL <$50

During the LAST 12 MONTHS, how often have you . . . taken something not belonging to you worth under $50?

1="Not At All" 2="Once" 3="Twice" 4="3 or 4 Times" 5="5 or More Times"

```{r}
tab1(ds3$V2285, cum.percent = TRUE)
```

### 06590:FRQ STEAL >$50

During the LAST 12 MONTHS, how often have you . . . taken something not belonging to you worth over $50?

1="Not At All" 2="Once" 3="Twice" 4="3 or 4 Times" 5="5 or More Times"

```{r}
tab1(ds3$V2286, cum.percent = TRUE)
```

### 06600:FRQ SHOPLIFT

During the LAST 12 MONTHS, how often have you . . . taken something from a store without paying for it?

1="Not At All" 2="Once" 3="Twice" 4="3 or 4 Times" 5="5 or More Times"

```{r}
tab1(ds3$V2287, cum.percent = TRUE)
```

### 06610:FRQ CAR THEFT

During the LAST 12 MONTHS, how often have you . . . taken a car that didn't belong to someone in your family without permission of the owner?

1="Not At All" 2="Once" 3="Twice" 4="3 or 4 Times" 5="5 or More Times"

```{r}
tab1(ds3$V2288, cum.percent = TRUE)
```

### 06620:FRQ STEAL CAR PT

During the LAST 12 MONTHS, how often have you . . . taken part of a car without permission of the owner?

1="Not At All" 2="Once" 3="Twice" 4="3 or 4 Times" 5="5 or More Times"

```{r}
tab1(ds3$V2289, cum.percent = TRUE)
```

### 06630:FRQ TRESPAS BLDG

During the LAST 12 MONTHS, how often have you . . . gone into some house or building when you weren't supposed to be there?

1="Not At All" 2="Once" 3="Twice" 4="3 or 4 Times" 5="5 or More Times"

```{r}
tab1(ds3$V2290, cum.percent = TRUE)
```

### 06640:FRQ ARSON

During the LAST 12 MONTHS, how often have you . . . set fire to someone's property on purpose?

1="Not At All" 2="Once" 3="Twice" 4="3 or 4 Times" 5="5 or More Times"

```{r}
tab1(ds3$V2291, cum.percent = TRUE)
```

### 06650:FRQ DMG SCH PPTY

During the LAST 12 MONTHS, how often have you . . . damaged school property on purpose?

1="Not At All" 2="Once" 3="Twice" 4="3 or 4 Times" 5="5 or More Times"

```{r}
tab1(ds3$V2292, cum.percent = TRUE)
```

### 06660:FRQ DMG WK PRPTY

During the LAST 12 MONTHS, how often have you . . . damaged property at work on purpose?

1="Not At All" 2="Once" 3="Twice" 4="3 or 4 Times" 5="5 or More Times"

```{r}
tab1(ds3$V2293, cum.percent = TRUE)
```



