---
title: "11_18_meeting_report"
author: "Siyang Ni"
date: "2022-11-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading datasets

```{r}
setwd("D:/research/Monitoring-The-Future/mtf_19_12")

load("D:/research/Monitoring-The-Future/mtf_19_12/DS0001/37841-0001-Data.rda")
core <- da37841.0001
rm(da37841.0001)

load("D:/research/Monitoring-The-Future/mtf_19_12/DS0002/37841-0002-Data.rda")
ds2 <- da37841.0002
rm(da37841.0002)

load("D:/research/Monitoring-The-Future/mtf_19_12/DS0003/37841-0003-Data.rda")
ds3 <- da37841.0003
rm(da37841.0003)

load("D:/research/Monitoring-The-Future/mtf_19_12/DS0004/37841-0004-Data.rda")
ds4 <- da37841.0004
rm(da37841.0004)

load("D:/research/Monitoring-The-Future/mtf_19_12/DS0005/37841-0005-Data.rda")
ds5 <- da37841.0005
rm(da37841.0005)

load("D:/research/Monitoring-The-Future/mtf_19_12/DS0006/37841-0006-Data.rda")
ds6 <- da37841.0006
rm(da37841.0006)

load("D:/research/Monitoring-The-Future/mtf_19_12/DS0007/37841-0007-Data.rda")
ds7 <- da37841.0007
rm(da37841.0007)

load("D:/research/Monitoring-The-Future/mtf_19_12/DS0008/37841-0008-Data.rda")
ds8 <- da37841.0008
rm(da37841.0008)

load("D:/research/Monitoring-The-Future/mtf_19_12/DS0009/37841-0009-Data.rda")
ds9 <- da37841.0009
rm(da37841.0009)

```

## Delinquency Variables

Load relevant packages

```{r}
library(epiDisplay)
```

### 00650:#X/12MO R TCKTD

Within the LAST 12 MONTHS, how many times, if any, have you received a ticket (OR been stopped and warned) for moving violations, such as speeding, running a stop light, or improper passing?

0="None" 1="Once" 2="Twice" 3="Three times" 4="Four or more times"

```{r}
tab1(core$V2197, cum.percent = TRUE)
tab1(ds2$V1197, cum.percent = TRUE)
tab1(ds3$V2197, cum.percent = TRUE)
tab1(ds4$V3197, cum.percent = TRUE)
tab1(ds5$V4197, cum.percent = TRUE)
tab1(ds6$V5197, cum.percent = TRUE)
tab1(ds7$V6197, cum.percent = TRUE)
```

### 06520:FRQ FIGHT PARNTS

how often have you . . . argued or had a fight with either of your parents?

1="Not At All" 2="Once" 3="Twice" 4="3 or 4 Times" 5="5 or More Times"
Data from the Western Region intentionally obliterated.

```{r}
tab1(ds3$V2279, cum.percent = TRUE)
```

### 06530:FRQ HIT SUPRVISR

During the LAST 12 MONTHS, how often have you . . . hit an instructor or supervisor?

1="Not At All" 2="Once" 3="Twice" 4="3 or 4 Times" 5="5 or More Times"

```{r}
tab1(ds3$V2280, cum.percent = TRUE)
```

### 06540:FRQ FGT WRK/SCHL

During the LAST 12 MONTHS, how often have you . . . gotten into a serious fight in school or at work?

1="Not At All" 2="Once" 3="Twice" 4="3 or 4 Times" 5="5 or More Times"

```{r}
tab1(ds3$V2281, cum.percent = TRUE)
```

### 06550:FRQ GANG FIGHT

During the LAST 12 MONTHS, how often have you . . . taken part in a fight where a group of your friends were against another group?

1="Not At All" 2="Once" 3="Twice" 4="3 or 4 Times" 5="5 or More Times"

```{r}
tab1(ds3$V2282, cum.percent = TRUE)
```

### 06560:FRQ HURT SM1 BAD

During the LAST 12 MONTHS, how often have you . . . hurt someone badly enough to need bandages or a doctor?

1="Not At All" 2="Once" 3="Twice" 4="3 or 4 Times" 5="5 or More Times"

```{r}
tab1(ds3$V2283, cum.percent = TRUE)
```

### 06570:FRQ THREAT WEAPN

During the LAST 12 MONTHS, how often have you . . . used a knife or gun or some other thing (like a club) to get something from a person?

1="Not At All" 2="Once" 3="Twice" 4="3 or 4 Times" 5="5 or More Times"

```{r}
tab1(ds3$V2284, cum.percent = TRUE)
```

### 06580:FRQ STEAL <$50

During the LAST 12 MONTHS, how often have you . . . taken something not belonging to you worth under $50?

1="Not At All" 2="Once" 3="Twice" 4="3 or 4 Times" 5="5 or More Times"

```{r}
tab1(ds3$V2285, cum.percent = TRUE)
```

### 06590:FRQ STEAL >$50

During the LAST 12 MONTHS, how often have you . . . taken something not belonging to you worth over $50?

1="Not At All" 2="Once" 3="Twice" 4="3 or 4 Times" 5="5 or More Times"

```{r}
tab1(ds3$V2286, cum.percent = TRUE)
```

### 06600:FRQ SHOPLIFT

During the LAST 12 MONTHS, how often have you . . . taken something from a store without paying for it?

1="Not At All" 2="Once" 3="Twice" 4="3 or 4 Times" 5="5 or More Times"

```{r}
tab1(ds3$V2287, cum.percent = TRUE)
```

### 06610:FRQ CAR THEFT

During the LAST 12 MONTHS, how often have you . . . taken a car that didn't belong to someone in your family without permission of the owner?

1="Not At All" 2="Once" 3="Twice" 4="3 or 4 Times" 5="5 or More Times"

```{r}
tab1(ds3$V2288, cum.percent = TRUE)
```

### 06620:FRQ STEAL CAR PT

During the LAST 12 MONTHS, how often have you . . . taken part of a car without permission of the owner?

1="Not At All" 2="Once" 3="Twice" 4="3 or 4 Times" 5="5 or More Times"

```{r}
tab1(ds3$V2289, cum.percent = TRUE)
```

### 06630:FRQ TRESPAS BLDG

During the LAST 12 MONTHS, how often have you . . . gone into some house or building when you weren't supposed to be there?

1="Not At All" 2="Once" 3="Twice" 4="3 or 4 Times" 5="5 or More Times"

```{r}
tab1(ds3$V2290, cum.percent = TRUE)
```

### 06640:FRQ ARSON

During the LAST 12 MONTHS, how often have you . . . set fire to someone's property on purpose?

1="Not At All" 2="Once" 3="Twice" 4="3 or 4 Times" 5="5 or More Times"

```{r}
tab1(ds3$V2291, cum.percent = TRUE)
```

### 06650:FRQ DMG SCH PPTY

During the LAST 12 MONTHS, how often have you . . . damaged school property on purpose?

1="Not At All" 2="Once" 3="Twice" 4="3 or 4 Times" 5="5 or More Times"

```{r}
tab1(ds3$V2292, cum.percent = TRUE)
```

### 06660:FRQ DMG WK PRPTY

During the LAST 12 MONTHS, how often have you . . . damaged property at work on purpose?

1="Not At All" 2="Once" 3="Twice" 4="3 or 4 Times" 5="5 or More Times"

```{r}
tab1(ds3$V2293, cum.percent = TRUE)
```


## Arrest Variable

### 25880:ARRSTD&TKN 2 POL

During the LAST 12 MONTHS, how often have you . . . been arrested and taken to a police station?

1="Not At All" 2="Once" 3="Twice" 4="3 or 4 Times" 5="5 or More Times"

```{r}
tab1(ds3$V2508, cum.percent = TRUE)

```

## Substance Use Variable

### 00760:EVR SMK CIG,REGL

Have you ever smoked cigarettes?

1="Never" 2="Once or twice" 3="Occasionally but not regularly" 4="Regularly in the past" 5="Regularly now"

```{r}
tab1(core$V2101, cum.percent = TRUE)
tab1(core$V2101D, cum.percent = TRUE)
tab1(ds2$V1208, cum.percent = TRUE)
tab1(ds4$V3101, cum.percent = TRUE)
tab1(ds5$V4101, cum.percent = TRUE)
tab1(ds6$V5101, cum.percent = TRUE)
tab1(ds7$V6101, cum.percent = TRUE)
```

### 00820:#X DRNK/LAST12MO

On how many occasions (if any) have you had alcoholic beverages to drink--more than just a few sips . . . during the last 12 months?

1="0 Occasions"  2="1-2 Occasions"   3="3-5 Occasions"  4="6-9 Occasions"  5="10-19 Occasions"  6="20-39 Occasions"  7="40 or More"

```{r}
tab1(core$V2105, cum.percent = TRUE)
tab1(core$V2105D, cum.percent = TRUE)
tab1(ds2$V1215, cum.percent = TRUE)
tab1(ds3$V2105, cum.percent = TRUE)
tab1(ds4$V3105, cum.percent = TRUE)
tab1(ds5$V4105, cum.percent = TRUE)
tab1(ds6$V5105, cum.percent = TRUE)
tab1(ds7$V6105, cum.percent = TRUE)
```

### 00860:#XMJ+HS/LAST12MO

On how many occasions (if any) have you used marijuana (grass, pot) or hashish (hash, hash oil) . . . during the last 12 months?

[For form 1, item is recoded from separate marijuana and hashish questions, and "Dope" is given as another example of what marijuana is called.]

1="0 Occasions" 2="1-2 Occasions" 3="3-5 Occasions" 4="6-9 Occasions" 5="10-19 Occasions" 6="20-39 Occasions" 7="40 or More"

```{r}
tab1(core$V2116, cum.percent = TRUE)
tab1(core$V2116D, cum.percent = TRUE)
tab1(ds2$V1116, cum.percent = TRUE)
tab1(ds3$V2116, cum.percent = TRUE)
tab1(ds4$V3116, cum.percent = TRUE)
tab1(ds5$V4116, cum.percent = TRUE)
tab1(ds6$V5116, cum.percent = TRUE)
tab1(ds7$V6116, cum.percent = TRUE)
```

### 00900:#X LSD/LAST 12MO

On how many occasions (if any) have you used LSD ("acid") . . . during the last 12 months?

[Worded slightly differently in form 1; see form 1 codebook.]

1="0 Occasions" 2="1-2 Occasions" 3="3-5 Occasions" 4="6-9 Occasions" 5="10-19 Occasions" 6="20-39 Occasions" 7="40 or More"

```{r}
tab1(core$V2119, cum.percent = TRUE)
tab1(core$V2119D, cum.percent = TRUE)
tab1(ds2$V1285, cum.percent = TRUE)
tab1(ds3$V2119, cum.percent = TRUE)
tab1(ds4$V3119, cum.percent = TRUE)
tab1(ds5$V4119, cum.percent = TRUE)
tab1(ds6$V5119, cum.percent = TRUE)
```

### 00960:#X COKE/LAST12MO

On how many occasions (if any) have you taken cocaine (sometimes called "coke", "crack", "rock") . . . during last 12 months?

[For questionnaire forms 1, 3, 4, and 6, item is recoded from separate questions about "crack" (items 22260-22280) and other forms of cocaine (items 22320-22340).]

```{r}
tab1(core$V2125, cum.percent = TRUE)
tab1(ds2$V1125, cum.percent = TRUE)
tab1(ds3$V2125, cum.percent = TRUE)
tab1(ds4$V3125, cum.percent = TRUE)
tab1(ds5$V4125, cum.percent = TRUE)
tab1(ds6$V5125, cum.percent = TRUE)
tab1(ds7$V6125, cum.percent = TRUE)
```

### 00990:#X AMPH/LAST12MO

{Amphetamines are sometimes prescribed by doctors for people who have trouble paying attention, are hyperactive, have ADHD, or have trouble staying awake. They are sometimes called uppers, ups, pep pills, and include drugs like Adderall and Ritalin. Drugstores are not supposed to sell them without a prescription from a doctor. Amphetamines

do NOT include any nonprescription drugs, such as over-the-counter diet pills or stay-awake pills.

[Questionnaire form 1 worded somewhat differently and also includes as examples: Benzedrine, Dexedrine, Methedrine, Ritalin, Adderall, Concerta, Methamphetamine, Meth or Crystal Meth (see form 1 codebook).]}

[All forms]: On how many occasions (if any) have you taken amphetamines on your own--that is, without a doctor telling you to take them . . . during the last 12 months?

1="0 Occasions" 2="1-2 Occasions" 3="3-5 Occasions" 4="6-9 Occasions" 5="10-19 Occasions" 6="20-39 Occasions" 7="40 or More"

```{r}
tab1(core$V2128, cum.percent = TRUE)
tab1(core$V2128D, cum.percent = TRUE)
tab1(ds2$V1330, cum.percent = TRUE)
tab1(ds3$V2128, cum.percent = TRUE)
tab1(ds4$V3128, cum.percent = TRUE)
tab1(ds5$V4128, cum.percent = TRUE)
tab1(ds6$V5128, cum.percent = TRUE)
tab1(ds7$V6128, cum.percent = TRUE)
```

### 01050:#X SED/BARB/LAST12MO

{Sedatives, including barbiturates, are sometimes prescribed by doctors to help people relax or get to sleep. They are sometimes called downs or downers, and include phenobarbital, Tuinal, Nembutal, and Seconal.} On how many occasions (if any) have you taken sedatives on your own--that is, without a doctor telling you to take them . . . during the last 12 months?

[Worded slightly differently in questionnaire form 1, and replaced Nembutal with Ambien, Lunesta, and Sonata as examples; see form 1 codebook.]

1="0 Occasions" 2="1-2 Occasions" 3="3-5 Occasions" 4="6-9 Occasions" 5="10-19 Occasions" 6="20-39 Occasions" 7="40 or More"

```{r}
tab1(core$V2134, cum.percent = TRUE)
tab1(core$V2134D, cum.percent = TRUE)
tab1(ds2$V1384, cum.percent = TRUE)
tab1(ds3$V2134, cum.percent = TRUE)
tab1(ds4$V3134, cum.percent = TRUE)
tab1(ds5$V4134, cum.percent = TRUE)
tab1(ds6$V5134, cum.percent = TRUE)
tab1(ds7$V6134, cum.percent = TRUE)
```

### 01080:#X TRQL/LAST12MO

{Tranquilizers are sometimes prescribed by doctors to calm people down, quiet their nerves, or relax their muscles. Librium, Valium, and Xanax are all tranquilizers.} On how many occasions (if any) have you taken tranquilizers on your own--that is, without a doctor telling you to take them . . . during the last 12 months?

[Questionnaire form 1 worded somewhat differently and adds Soma, Serax, Ativan, Klonopin to the examples (see form 1 codebook).]

1="0 Occasions" 2="1-2 Occasions" 3="3-5 Occasions" 4="6-9 Occasions" 5="10-19 Occasions" 6="20-39 Occasions" 7="40 or More"

```{r}
tab1(core$V2137, cum.percent = TRUE)
tab1(core$V2137D, cum.percent = TRUE)
tab1(ds2$V1431, cum.percent = TRUE)
tab1(ds3$V2137, cum.percent = TRUE)
tab1(ds4$V3137, cum.percent = TRUE)
tab1(ds5$V4137, cum.percent = TRUE)
tab1(ds6$V5137, cum.percent = TRUE)
tab1(ds7$V6137, cum.percent = TRUE)
```

### 01110:#X 'H'/LAST 12MO

On how many occasions (if any) have you taken heroin . . . during the last 12 months?

[For questionnaire forms 2, 5, and 6, item is recoded from separate questions about heroin use with a needle (items 29630-29650) and without a needle (items 29660-29680).]

1="0 Occasions" 2="1-2 Occasions" 3="3-5 Occasions" 4="6-9 Occasions" 5="10-19 Occasions" 6="20-39 Occasions" 7="40 or More"

```{r}
tab1(core$V2140, cum.percent = TRUE)
tab1(ds2$V1522, cum.percent = TRUE)
tab1(ds3$V2140, cum.percent = TRUE)
tab1(ds4$V3140, cum.percent = TRUE)
tab1(ds5$V4140, cum.percent = TRUE)
tab1(ds6$V5140, cum.percent = TRUE)
tab1(ds7$V6140, cum.percent = TRUE)
```

### 01140:#X NARC/LAST12MO

{There are a number of narcotics other than heroin, such as methadone, opium, morphine, codeine, Demerol, Vicodin, OxyContin, and Percocet. These are sometimes prescribed by doctors.} On how many occasions (if any) have you taken narcotics other than heroin on your own--that is, without a doctor telling you to take them . . . during the last 12 months?

[Questionnaire form 1 worded somewhat differently and adds "Percodan, Ultram" (see form 1 Codebook).]

1="0 Occasions" 2="1-2 Occasions" 3="3-5 Occasions" 4="6-9 Occasions" 5="10-19 Occasions" 6="20-39 Occasions" 7="40 or More"


```{r}
tab1(core$V2143, cum.percent = TRUE)
tab1(core$V2143D, cum.percent = TRUE)
tab1(ds2$V1566, cum.percent = TRUE)
tab1(ds3$V2143, cum.percent = TRUE)
tab1(ds4$V3143, cum.percent = TRUE)
tab1(ds5$V4143, cum.percent = TRUE)
tab1(ds6$V5143, cum.percent = TRUE)
tab1(ds7$V6143, cum.percent = TRUE)
```

### 00170:#X INHL/LAST12MO
On how many occasions (if any) have you sniffed glue, or breathed the contents of aerosol spray cans, or inhaled any other gases or sprays in order to get high . . . during the last 12 months?

1="0 Occasions" 2="1-2 Occasions" 3="3-5 Occasions" 4="6-9 Occasions" 5="10-19 Occasions" 6="20-39 Occasions" 7="40 or More"

```{r}
tab1(core$V2146, cum.percent = TRUE)
tab1(core$V2146D, cum.percent = TRUE)
tab1(ds3$V2146, cum.percent = TRUE)
tab1(ds4$V3146, cum.percent = TRUE)
tab1(ds6$V5146, cum.percent = TRUE)
```

### 22700:#X STRD/LAST12MO

{Anabolic steroids are prescription drugs sometimes prescribed by doctors to treat certain conditions. Some athletes, and others, have used them to try to increase muscle development.} On how many occasions (if any) have you taken steroids on your own--that is, without a doctor telling you to take them . . . during the last 12 months?

1="0 Occasions" 2="1-2 Occasions" 3="3-5 Occasions" 4="6-9 Occasions" 5="10-19 Occasions" 6="20-39 Occasions" 7="40 or More"

```{r}
tab1(core$V2494, cum.percent = TRUE)
tab1(ds6$V5528, cum.percent = TRUE)
tab1(ds7$V6369, cum.percent = TRUE)
```

### 35150:#DAYS VAPE NIC/12MO

On how many DAYS (if any) have you vaped NICOTINE . . . during the last 12 months?

1="0 Days" 2="1-2 Days" 3="3-5 Days" 4="6-9 Days" 5="10-19 Days" 6="20 or More"

```{r}
tab1(core$V2581, cum.percent = TRUE)
tab1(ds2$V1978, cum.percent = TRUE)
tab1(ds3$V2581, cum.percent = TRUE)
tab1(ds5$V4472, cum.percent = TRUE)
tab1(ds7$V6642, cum.percent = TRUE)
```

### V2584: 35180:#DAYS VAPE MJ/12MO

On how many DAYS (if any) have you vaped MARIJUANA . . . during the last 12 months?

1="0 Days" 2="1-2 Days" 3="3-5 Days" 4="6-9 Days" 5="10-19 Days

```{r}
tab1(core$V2584, cum.percent = TRUE)
tab1(ds2$V1981, cum.percent = TRUE)
tab1(ds3$V2584, cum.percent = TRUE)
tab1(ds5$V4475, cum.percent = TRUE)
tab1(ds7$V6645, cum.percent = TRUE)
```






